---
title: "Journals in the set"
output: 
  html_notebook: default
  github_document: default
---

```{r setup, include = FALSE}
library(tidyverse)
library(lubridate)

articles <- filter(read_csv("data/master.csv"), print_publication_date >= '2013-01-01')
mentions <- filter(read_csv("data/mentions.csv"), date_posted >= "2012-06-30")
open_closed <- filter(read_csv("data/open_closed.csv"))
open_closed_articles <- filter(left_join(articles, open_closed), !is.na(known_to_be_open))
open_closed_with_mentions <- left_join(open_closed_articles, mentions)
```

Which are the most commonly Mentioned journals for closed articles?

```{r Policy citations in journals for closed Articles}

journals_with_closed_articles <- filter(open_closed_with_mentions, source == 'policy', known_to_be_open == 'FALSE') %>%
                                  group_by(journal_title) %>%
                                  summarise(total_articles = n())

arrange(journals_with_closed_articles, desc(total_articles))

```

Which are the most commonly Mentioned journals for open articles?

```{r Policy citations in journals for open Articles}

journals_with_open_articles <- filter(open_closed_with_mentions, source == 'policy', known_to_be_open == 'TRUE') %>%
                                  group_by(journal_title) %>%
                                  summarise(total_articles = n())

arrange(journals_with_open_articles, desc(total_articles))

```

Note: PNAS isn't 'open' open (as they don't publish with a CC license) so: this has implications for how Dimensions get their 'open vs closed' data (i.e. from Unpaywall)... Is this because the papers were downloaded from a repository rather than the PNAS website?

```{r PNAS Papers download location}

pnas_papers <- filter(open_closed_articles, journal_title == "Proceedings of the National Academy of Sciences of the United States of America")
                
select(pnas_papers, article_title, known_to_be_open, open_access_status)

```

However, the above indicates that Unpaywall / Dimensions got the papers from PNAS's own website - hence their definition of 'open' is a little different.

Unpaywalled does not make judgements about what constitutes an open access article - if it is freely available online then it is open access in their book which means the PNAS open access option is compliant. I suppose this doesn't really matter in the terms of policy inclusion as it is the free availability of the article that is important rather than what licence it has etc.



