---
title: "Policy Mentions in Open and closed Articles"
output: 
  html_notebook: default
  github_document: default
---

```{r setup, include = FALSE}
library(tidyverse)
articles <- read_csv("data/master.csv")
mentions <- read_csv("data/mentions.csv")
open_closed <- read_csv("data/open_closed.csv")
open_closed_articles <- left_join(articles, open_closed)
open_closed_with_mentions <- left_join(open_closed_articles, mentions)
```


This is where we shall start to investigate the impact of Openness on the use of articles in policy. We want to know if open articles have more policy mentions than closed articles. This is the basic question but we should also factor in time since publication.

# Simple how many are open v how many are closed
```{r open v closed}
summarise(
group_by(open_closed_articles, known_to_be_open),
total = n()
)
```

# ordering by number of policy mentions
```{r order by policy mentions}
arrange(
summarise(
  group_by(filter(open_closed_with_mentions, source == "policy"), 
           article_title),
  total = n()
), 
desc(total))
```



# average number of policy mentions
```{r average policy mentions}
policy_mention_totals <- summarise(
  group_by(filter(open_closed_with_mentions, source == "policy"), 
           doi),
  policy_mention_total = n(),
)
articles_with_policy_totals <- left_join(open_closed_articles, policy_mention_totals)

summarise(
  group_by(articles_with_policy_totals, known_to_be_open),
  average_policy_mentions = mean(policy_mention_total)
)

```

# average time to first policy mention in open versus closed articles


