---
title: "Policy Mentions in Open and closed Articles"
output: 
  html_notebook: default
  github_document: default
---

```{r setup, include = FALSE}
library(tidyverse)
library(lubridate)

articles <- filter(read_csv("data/master.csv"), print_publication_date >= '2013-01-01')
mentions <- filter(read_csv("data/mentions.csv"), date_posted >= "2012-06-30")
open_closed <- filter(read_csv("data/open_closed.csv"))
open_closed_articles <- filter(left_join(articles, open_closed), !is.na(known_to_be_open))
open_closed_with_mentions <- left_join(open_closed_articles, mentions)
```


We discovered that the print_publication_dates contained many before the lower date of 2013 - there's a filter applied to the read above. We think this is because of Scopus's filter / information about publication dates being different to Altmetric's.

This is where we shall start to investigate the impact of Openness on the use of articles in policy. We want to know if open articles have more policy mentions than closed articles. This is the basic question but we should also factor in time since publication.

# Simple how many are open v how many are closed
```{r open v closed}
summarise(
group_by(open_closed_articles, known_to_be_open),
total = n()
)
```

# ordering by number of policy mentions
```{r order by policy mentions}
arrange(
summarise(
  group_by(filter(open_closed_with_mentions, source == "policy"), 
           article_title),
  total = n()
), 
desc(total))
```



# average number of policy mentions
```{r average policy mentions}
policy_mention_totals <- summarise(
  group_by(filter(open_closed_with_mentions, source == "policy"), 
           doi),
  policy_mention_total = n(),
)
articles_with_policy_totals <- left_join(open_closed_articles, policy_mention_totals)

summarise(
  group_by(articles_with_policy_totals, known_to_be_open),
  average_policy_mentions = mean(policy_mention_total, na.rm = TRUE),
  sd_policy_mentions = sd(policy_mention_total, na.rm = TRUE)
)

```

# average time to first policy mention in open versus closed articles

The below filters out just the policy mentions, groups them and summarises on the min(date_posted) to give us the earliest policy mention.

Then it subtracts the date of publication from the first policy mention date to give us the number of days between publication and mention in a policy.

And then it takes and average and standard deviation of those times for open and closed papers.

The SD indicates that it is better to publish in a closed journal if you want your paper cited in policy quicker... Why might that be?

```{r Average time to first policy mention}

open_closed_with_first_policy_mention <- filter(open_closed_with_mentions, source == 'policy') %>%
                                          group_by(article_title, journal_title, print_publication_date, known_to_be_open) %>%
                                          summarise(first_policy_pub_date = min(date_posted)) %>%
                                          mutate(
                                             days_to_first_policy_mention = as_date(first_policy_pub_date) - as_date(print_publication_date) 
                                          )

summarise(
  group_by(open_closed_with_first_policy_mention, known_to_be_open),
  mean_average_days_to_first_policy_mention = mean(days_to_first_policy_mention, na.rm = TRUE),
  sd_average_days_to_first_policy_mention = sd(days_to_first_policy_mention, na.rm = TRUE)
)

```



